### 2021-09-23 paper/paper.tex
project-brief: finish background and significance

In addition, this type of typing is frequently taught in the beginner level.
However, finger position is not \parencite{donica2018}

There is currently no way to automatically detect which finger is used during
typing. No hardware or software solutions currently exist in the market. This
research aims to solve this by combine finger tracking, with educational typing
tests to determine which finger pressed the key and if that finger is the
correct one to use.

\section{Significance of the Research}
This research is beneficial for all users of physical keyboards. These include a
vast majority of the population as there are a lot of professions that heavily
rely on keyboards. Examples include developers, physicians, educators,
accountants.

This research has a direct impact on people that has onset RSI or other
hand/wrist injuries [ statistics ] that are caused by poor typing habits. By
correcting these poor habits, pain from these injuries will be lessened, and
even be prevented from occurring in the first place.

>>>>

In addition, this type of typing is frequently taught in the beginner level
\parencite{donica2018}. This means that there is a need to weed out bad habits
that may develop, like using the index finger for pressing the spacebar or
backspace. However, it is impractical for an educator to check each individual
student if they are not performing these movements as these may only show for a
specific which may not be common.

Thus, there is a need for automatically detecting which finger is used during
typing, and for the position of the wrist in relation to the arm. One way to do
this is through finger and hand tracking. One solution for tracking is by using
image processing and machine learning. An example of this is MediaPipe by
\cite{mediapipe}.

MediaPipe allows for various applications for machine learning in the field of
image processing. This includes, hand tracking, pose estimation, object
detection, and others. Another example of a library that allows for hand and
finger tracking is OpenCV by \cite{opencv}. This is a tool that simplifies for
computer vision, and image processing. Machine learning can also be used with
OpenCV.

This research aims to improve touch typing training by combining hand and finger
tracking, with educational typing tests to determine if the finger used to type
is correct and if the overall posture of the hand ergonomic and healthy.

\section{Significance of the Research}
This research is beneficial for all users of physical keyboards. These include a
vast majority of the population as there are a lot of professions that heavily
rely on keyboards. Examples include developers, physicians, educators,
accountants. By having better ergonomics while typing, wrist injuries can be
prevented, and typing speed may be increased

This research also helps educators, especially early educators teaching beginner
typers. By automatically checking for ergonomics and posture, the burden of
checking each individual students is lessened, and directed interventions for
bad habits can be easily created as students with these bad habits are easily
identified

This research has a direct impact on people that has onset RSI or other
hand/wrist injuries that are caused by poor typing habits. By correcting these
poor habits, pain from these injuries will be lessened, and even be prevented
from occurring in the first place. A specific example of this is by reducing
ulnar deviation which affects the nerve that is indicative of CTS
\parencite{toosi2015}.
